\bf Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-06-23 paper.qmd
Updated figure title for remove low-density hexagons

## To obtain the standardise counts within hexbins
counts_df1 <- hb_obj_scurve1$std_cts
df_bin_centroids1 <- extract_hexbin_centroids(
  centroids_df = all_centroids_df1, 
  counts_df = counts_df1)

@@

## To obtain the standardise counts within hexbins
counts_df2 <- hb_obj_scurve2$std_cts
df_bin_centroids2 <- extract_hexbin_centroids(
  centroids_df = all_centroids_df2, 
  counts_df = counts_df2)

@@

## To obtain the standardise counts within hexbins
counts_df3 <- hb_obj_scurve3$std_cts
df_bin_centroids3 <- extract_hexbin_centroids(
  centroids_df = all_centroids_df3, 
  counts_df = counts_df3)

@@

```{r}
#| echo: false
#| label: fig-lwd-scurve
#| fig-pos: H
#| fig-cap: "(a) Identification of low-density hexagons using a benchmark value of $0.242$, and (c) Identification of low-density hexagons considering neighboring bins."
#| fig-width: 9
#| fig-height: 6

>>>>

## To obtain the standardise counts within hexbins
counts_df1 <- hb_obj_scurve1$std_cts
df_bin_centroids1 <- extract_hexbin_centroids(
  centroids_df = all_centroids_df1, 
  counts_df = counts_df1) |>
  filter(drop_empty == FALSE)

@@

## To obtain the standardise counts within hexbins
counts_df2 <- hb_obj_scurve2$std_cts
df_bin_centroids2 <- extract_hexbin_centroids(
  centroids_df = all_centroids_df2, 
  counts_df = counts_df2) |>
  filter(drop_empty == FALSE)

@@

## To obtain the standardise counts within hexbins
counts_df3 <- hb_obj_scurve3$std_cts
df_bin_centroids3 <- extract_hexbin_centroids(
  centroids_df = all_centroids_df3, 
  counts_df = counts_df3) |>
  filter(drop_empty == FALSE)

@@

```{r}
#| echo: false
#| label: fig-lwd-scurve
#| fig-pos: H
#| fig-cap: "Two approaches to identify low-density hexagons. Hexagon grid (a) marks hexagons with a standardized count less than $0.25$. Hexagon grid (b) marks hexagons by considering the densities of neighboring bins. Removing hexagons by also investigating the densities of neighboring bins is more reliable for preserving the structure."
#| fig-width: 9
#| fig-height: 6

### 2024-06-23 paper.tex
Updated figure title for remove low-density hexagons

\caption{\label{fig-lwd-scurve}(a) Identification of low-density
hexagons using a benchmark value of \(0.242\), and (c) Identification of
low-density hexagons considering neighboring bins.}

>>>>

\caption{\label{fig-lwd-scurve}Two approaches to identify low-density
hexagons. Hexagon grid (a) marks hexagons with a standardized count less
than \(0.25\). Hexagon grid (b) marks hexagons by considering the
densities of neighboring bins. Removing hexagons by also investigating
the densities of neighboring bins is more reliable for preserving the
structure.}
